Blame and Coercion: Together Again for the Second Time

### 2019-10-16 paper.tex
check

In this section we review the normal coercion (NC) in 
\citet{siek2012interpretations}. We ignore sum types and product types in this 
section, because they were not presented in the paper. We assume a basic 
familiarity with coercion, and direct readers who do not know it to 
\citet{siek2012interpretations}.

As the name suggests, 
hypercoercion is largely inspired by coercion, especially its subst NC. We 
will highlight the similarity of normal coercion and hypercoercion, and hope 
this would convince you that hypercoercion should be as difficult to implement 
as NC.

@@

\figref{fig:normal-coercion} defines the normal coercion. 
Types, pre-types, and blame labels are as before.
Let $ I $ ranges over injectable types. An injectable type is a type that can 
be cast directly to (injection) and from (projection) $ \TOOdyn $. The 
definition of injectable type depends on blame strategy. With \lazyD, all 
pre-types are injectable. With \lazyUD, only $ \POOfun{\TOOdyn}{\TOOdyn} $ 
is injectable. 
Let $ c $ ranges over coercions, a coercion is either injection, projection, 
identity, failure, sequencing, or function coercion.
Let $ \bar{c} $ ranges over wrapper coercions, which represent casts in $ 
\vOOcast{v}{c} $.
Let $ \hat{c} $ ranges over normal coercions. If we inline $ \bar{c} $ and 
re-arrange cases a little bit, the definition becomes:
\[
\begin{array}{rclr}
\stxrule{\hat{c}}{normal coercions}{
	\ncFun{\hat{c}}{\hat{c}} \mid
	\ncSeq{\ncProj{I}{l}}{\ncFun{\hat{c}}{\hat{c}}} \mid
	\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}} \mid
	\ncSeq{\ncProj{I}{l}}{\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}} \mid
	\ncSeq{\ncProj{I}{l}}{\ncFail{l}}
}
\stxrulecont{
	\ncId \mid
	\ncProj{I}{l} \mid
	\ncInj{I} \mid
	\ncSeq{\ncProj{I}{l}}{\ncInj{I}} \mid
	\ncFail{l} \mid
}
\end{array}
\]

Three observations on this definition leads to hypercoercion: 
\begin{enumerate}
	\item The length of normal coercion is at most three.
	\item Projections are always at the beginning when presented.
	\item Injections and failures are always at the end when presented.
\end{enumerate}

@@

>>>>

In this section we review the normal coercions (NC) of 
\citet{siek2012interpretations}.
\todo[inline]{Don't abbreviate to NC. -Jeremy}
We ignore sum types and product types in this 
section, because they were not presented in the paper. We assume a basic 
familiarity with coercion, and direct readers who do not know it to 
\citet{siek2012interpretations}.

As the name suggests, 
hypercoercion is largely inspired by coercion, especially its subst NC.
\todo[inline]{``subst'' is not a word.}
We 
will highlight the similarity of normal coercion and hypercoercion, and hope 
this would convince you that hypercoercion should be as difficult to implement 
as NC.

\todo[inline]{I don't think we should try to convince the reader that
  hypercoercions are easier to implement. We don't have real evidence
  for that.}

@@

\figref{fig:normal-coercion} defines the normal coercion.
\todo[inline]{Give a summary statement about the shape of the normal form.}
Types, pre-types, and blame labels are as before.
Let $ I $ ranges over injectable types. An injectable type is a type that can 
be cast directly to (injection) and from (projection) $ \TOOdyn $. The 
definition of injectable type depends on blame strategy. With \lazyD, all 
pre-types are injectable. With \lazyUD, only $ \POOfun{\TOOdyn}{\TOOdyn} $ 
is injectable. 
Let $ c $ ranges over coercions, a coercion is either injection, projection, 
identity, failure, sequencing, or function coercion.
Let $ \bar{c} $ ranges over wrapper coercions, which represent casts in $ 
\vOOcast{v}{c} $.
Let $ \hat{c} $ ranges over normal coercions. If we inline $ \bar{c} $ and 
re-arrange cases a little bit, the definition becomes:
\todo[inline]{Be more specific than ``a little bit''. -Jeremy}
\[
\begin{array}{rclr}
\stxrule{\hat{c}}{normal coercions}{
	\ncFun{\hat{c}}{\hat{c}} \mid
	\ncSeq{\ncProj{I}{l}}{\ncFun{\hat{c}}{\hat{c}}} \mid
	\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}} \mid
	\ncSeq{\ncProj{I}{l}}{\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}} \mid
	\ncSeq{\ncProj{I}{l}}{\ncFail{l}}
}
\stxrulecont{
	\ncId \mid
	\ncProj{I}{l} \mid
	\ncInj{I} \mid
	\ncSeq{\ncProj{I}{l}}{\ncInj{I}} \mid
	\ncFail{l} \mid
}
\end{array}
\]

Three observations on this definition leads to hypercoercion: 
\begin{enumerate}
	\item The length of normal coercion is at most three.
	\item Projections are always at the beginning when presented.
          \todo[inline]{change ``presented'' to ``present''. }
	\item Injections and failures are always at the end when presented.
          \todo[inline]{change ``presented'' to ``present''. }
\end{enumerate}

@@

\todo[inline]{What is the main idea behind the organization of
 hypercoercions?}
